Double, Double, Spin plus Nubble: Two Stars and Two Signals in PTFO 8-8695

### 2020-04-26 paper/ms.tex
Update ms.tex
Having fun editing
Fun, fun, fun

%\title{Against the Planetary Interpretation of PTFO$\,$8-8695b}
% \title{Seeing Double: Still Against the Planetary Interpretation of
% PTFO$\,$8-8695b}
% \title{Seeing Double: TESS and Gaia Show That PTFO$\,$8-8695b is Unlikely a
% Planet}
%\title{Seeing Double: Indications From {\it TESS} and {\it Gaia} That
%PTFO$\,$8-8695b is Not a Planet}
%\title{Double Trouble: Transient Dips and Photometric Binarity in
%PTFO$\,$8-8695}
\title{Double, Double, Spin plus Nubble: Two Stars and Two Signals in
PTFO 8-8695}

@@

%
% key authors:
%
\author[0000-0002-0514-5538]{L. G. Bouma}
\affiliation{ Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0002-4265-047X]{J. N. Winn}
\affiliation{ Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}

\begin{abstract}
  PTFO$\,$8-8695b is a candidate hot Jupiter in the 7--10 million year
  old Orion-OB1a cluster. We inspected data from TESS and Gaia to
  clarify whether it is truly a planet.  The Gaia data show that
  PTFO$\,$8-8695 is a photometric binary with respect to members of
  its kinematic group, and independently suggest that it is an
  astrometric binary.  The TESS lightcurve shows that the dominant
  variability in this system is sinusoidal with a long period $P_{\rm
  \ell}=11.96\,$hr, presumably caused by stellar rotation.  Also
  present is a combined dip and asymmetric sinusoid, previously
  identified as the planet candidate, that repeats with a short period
  $P_{\rm s}= 10.74\,$hr.  The two signals beat every 4.48 days.
  Although there is a dip in the short-period signal, ground-based
  photometry from the past decade indicates that the orbital phase of
  the dip seems to have instantaneously jumped, at least once, and
  perhaps twice.  Planets do not ``jump'' in orbital phase.  Given the
  available evidence, we believe that PTFO$\,$8-8695 is a binary M
  dwarf in which one star shows the long rotation signal, and the
  other star shows transient dipping that has been seen in a few other
  young low-mass stars.  The origin of these transient dips is still
  undetermined.
\end{abstract}

>>>>

%\title{Against the Planetary Interpretation of PTFO$\,$8-8695b}
% \title{Seeing Double: Still Against the Planetary Interpretation of
% PTFO$\,$8-8695b}
% \title{Seeing Double: TESS and Gaia Show That PTFO$\,$8-8695b is Unlikely a
% Planet}
%\title{Seeing Double: Indications From {\it TESS} and {\it Gaia} That
%PTFO$\,$8-8695b is Not a Planet}
%\title{Double Trouble: Transient Dips and Photometric Binarity in
%PTFO$\,$8-8695}
\title{Double, Double, Spin plus Nubble: Two Stars and Two Signals in
PTFO 8-8695}
\title{PTFO\,8-8695: A binary star, not a hot Jupiter host}

@@

%
% key authors:
%
\author[0000-0002-0514-5538]{L. G. Bouma}
\affiliation{ Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0002-4265-047X]{J.\,N.\,Winn}
\affiliation{ Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}

\begin{abstract}
  PTFO$\,$8-8695 is a star in the 7--10 million year
  old Orion-OB1a cluster that shows brightness dips that resemble planetary transits.
  While strong evidence against the planet hypothesis has already been provided,
  the possibility remains debated in the literature.
  To obtain further clues, we inspected data from the
  NASA {\it Transiting Exoplanet Survey Satellite} (TESS) and the ESA Gaia mission.
  The Gaia data show that
  PTFO$\,$8-8695 is a photometric binary with respect to members of
  its kinematic group, and independently suggest that it is an
  astrometric binary.  The TESS lightcurve shows two different photometric
  periods. The variability is dominated by a sinusoidal signal with a period
  of 11.96\,$hr, presumably caused by stellar rotation.  Also
  present is a 10.74-day signal consisting of a not-quite sinusoid interrupted
  by 1.2\% hour-long dips, the type of signal previously
  intepreted as planetary transits.
  The phase of the dips is nearly 180$^\circ$ away from the phase of the originally reported dips,
  which, as noted previously, makes them difficult to explain as planetary transits.
  Instead, we believe that PTFO$\,$8-8695 is a pair of young
  and rapidly rotating M dwarfs, one of which shows the same ``transient-dipper''
  behavior that been seen in at least 5 other cases.
  The origin of these transient dips is still unknown but likely involves circumstellar material.
\end{abstract}
